Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654

### 2016-06-19 WRITEUP/Intro.tex
moved stuff to ms.tex and slightly reorganized intro sec

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

\citestyle{aa}
\shorttitle{TBD}
\shortauthors{Leung \& Riechers}

\begin{document}
%{\tiny  \RevisionInfo}

\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
\end{abstract}

\section{Introduction} 
The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
$z_\textrm{AGN,HST}$ = 
0.658, respectively \citep{}

% FG gal is an elliptical gal: Slues+03 absorption lines

As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with
Einstein ring of size 1\farcs83 in radius. The 
background AGN is lensed into 4 point-like image A,B,C,D on a ring (emission
from the AGN host galaxy) around G, the foreground galaxy. 
C06 report the redshift of the background AGN of 0.658 with magnification ~ 9,
claimed Seyfert 1 spiral galaxy.

In this paper, we BLAH, refining the redshift to $z$=0.654
We use a cosmology WMAP9.

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ =
0.654
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
(Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest-frame 3.6 mm), employing
a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 (BP) , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
% 1124-186(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
% (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for
pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as bandpass calibrators 
for both tracks.
MWC349 and 3C279 were observed
as the primary
absolute flux calibrator for C and D array observations, respectively, yielding
$\lesssim
$15\% calibration accuracy.

The GILDAS package was used to reduce and analyze the visibility data which are
then imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise
is $\sigma$ =
0.177 
Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
(21.5 km s$^{-1}$) . 
The continuum image is created by % 2.152 mm; 
averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
% set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
% combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) 
%toward the background galaxy RXJ1131-1231 at $z$ = 0.654
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) on 2014 February 17 
under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations.  The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17.9 km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
flagging poor visibility data. 
The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary
absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks. 
% poor phase note
Since the phase calibrator from the first track is faint and was observed under
poor weather and the phase calibrator used for the second track was
far from our target source.
Hence, the phase calibration was 
subpar, with rms scatter $\sim$ 60\degr. 
We estimate $\sim
$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and 
the calibrated phase scatter.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final 
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

\subsection{VLA} 
% 20081229
% flux 1331+305
% phase 1130-149

Observations of the radio continuum toward the
galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large 
Array (VLA; Program ID: AW741; PI: Wucknitz).
Observations were carried out on BLAH under excellent/GOOD? weather
conditions in the A array configurations. The C-Band receivers were used to 
cover the BLAH
, employing a correlator setup providing a bandwidth of BLAH GHz in each
sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time
after 
discarding unusable visibility data.

The nearby radio quasar BLAH was observed every BLAH minutes for
pointing, amplitude, and phase calibration, and BLAH was observed as the
primary
absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding
$\sim
$15\% calibration accuracy.
The AIPS package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final
rms 
noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.

\section{HST astrometry}
We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
latter to the east by 0\farcs5963 in R.A and +0\farcs8372 in declination., which is consistent with the typical astrometric precision of the HST image. 
The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas. 
We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.

%The astrometry of the HST images was firstly calibrated against a wider-field
%optical image of the cluster which had in turn been aligned onto the FK5
%coordinate system to an rms precision of ~0.2".

\section{CO($J$ = 3 $\rightarrow$ 2) line emission}

% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
%  57.753459930419922        10.658399798838524
% 38.906448364257812        54.223567641493943
% 258.26144409179688        57.450322398332851
% 2.2153112888336182        2.9563491085933622

% If we fit gaussian without the continuum to minimize error:
% 58.848747253417969        10.030933764224825
% 36.368530273437500        54.749284630860281
% 276.93515014648438        54.753666156237443

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231.
We extract the spectrum and fit a single-component Gaussian as shown in Figure
\ref{fig:co32spec}
yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
\caption{
CO32 line spectrum
 \label{fig:co32spec}}
\end{figure}

% line free channels:1,118,160,600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

At spatial position of CO emission, No significant continuum emission was
detected from the line-free channels down to a 3$\sigma$ limit of 2.49mJy Beam\pmOne.
(also as suggested in the fitted Gaussian to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CO($J$ = 2 $\rightarrow$ 1) line emission}

% intensity over chan 124, 156 of rms ~ 1.451 mJy/ Beam/ch
% velocity resolution per bin: 21.528154 km/s

%sigma_mom0 = 0.43  over chan: 127, 155

We detect dynamically resolved CO($J$ = 2 $\rightarrow$ 1) line emission toward
the background galaxies in RXJ1131-1231.

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
velocity-integrated 
CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ 0.2 Jy km s$^{-1}$.

We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam. Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne. 
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
velocity range in z=0 frame = [-530.33, 72.73] \kms
chan = [127, 155] 
sigma = 0.16821825 Jy \kms per Beam
theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
 \label{fig:highOmoments}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
\caption{
Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
position of the foreground lensing galaxy (component G) as detected in the HST image.
 \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
\caption{ 
Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
 \label{fig:spatialSpec}}
\end{figure*}

\section{Continuum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PdBI
% 2mm continuum averaged over chan 1 120 165 360
% number of channels = 316
% sigma = 1.451 mJy/B / sqrt(316) = 0.081625 mJy/B 
% go noise on map (whole map) after cleaning: 89.274 µJy/B
% F = 1.2 mJy (integrated spatially, from ~ 1 sigma contour; 150 pixels)
%
% 2mm peak is centered on foreground galaxy ~ 799 µJy/B --> with C band --> spectral index
%	- 2mm marginally resolved along one axis (arc)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% VLA C Band
%

VLA C Band continuum image shows resolved jets and core emission from the foreground lensing galaxy as well as the background lensed quasar (as arcs). We extracted the 5GHz fluxes for the arcs and the core as listed in Table \ref{tab:photometry}.

As shown in Figure \ref{fig:cont}, we detect 2mm continuum emission toward both the foreground galaxy and the background as lensed emission.  
The integrated continuum flux density is 1.2 mJy, while the peak emission is centered on the foreground galaxy at $S_\nu$ of 8 \micron Jy beam\pmOne.  The detection is hence marginally resolved along one axis as shown in Figure \ref{fig:contco21}. 
We attempted to extract the background emission by subtracting the foreground emission as modeled by a point source (unresolved). But the residual after removing a point source model is just noise. So we I guess if we take the difference between the integrated and the  peak in the image plane is an upper limit to the background source at 2mm, which is $\sim$ 0.4 mJy.

We fit power law to the VLA radio data and the 2mm continuum, we derive a spectral index of $\alpha$=0.025.
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
\caption{CO 21 moment0 overlay on 2mm continuum.  % chan [127,155]	
TODO: add the beam
 \label{fig:contco21}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/Cont2mm_5GHz_double.eps}    
\caption{VLA 5GHz continuum and PdBI 2mm continuum
 \label{fig:cont}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{
can kill left figure eventually by combining this to ContCO21.eps
Right: alignment of HST and VLA 5 GHz continuum
 \label{fig:}}
\end{figure*}

\section{\rot{2}{1} Lens model}

\subsection{interpretation}
- C06 suggest the presence of an interacting dusty galaxy in their HST
observations, which BJB+08 calls it the F component. The lensed images of the
ABCDE 
components coincide with our CO data (see mom0 on HST and channel map),
evidently CO emission coming from the AGN host galaxy. 
- one of the red channels in our lens model suggests a second source component,
which is consistent with the spatially offset dusty source (see mom0 on HST,
which 
the red velocity component coincides with this F component)

%%%%%%%%%%%%%%%%%%%%%%%%
We compare our lens model parameters on the mass distribution of the lensing
galaxy with literature, particularly against the SIE model presented by C06. 
In C06, their SIE model shows position of lensing mass is offset by (-0.015",
-0.041" from obsservations (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
theta\_R = 1.84" $\pm$ 0.01. 
Our best-fit model parameters finds a BLAH
	- Our model lens parameters (median):
		- file: WRITEUP/MedianLensModelParams.txt
		- lensing gal. position is consistent with C06, 
		- Einstein radius: consistent with C06
		- PA: consistent within errors
		- Axial ratio: consistent within errors
%%%%%%%%%%%%%%%%%%%%%%%%%

Differential lensing is at play as suggested by the spectral shape of the \rot{2}{1} line profile, where 
flux density in the red wing is much high than in the blue wing.  
We modelled the emission using different kinematic components, the magnification factors are reported in Table BLAH.
\input{table_magFactor}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
\caption{
Pseudo observed 0th moment map in the lens plane. (left)
Pseudo 0th moment map in the source plane. (right)
\label{fig:}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.65\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.65\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
of channel widths $\sim$ 100\kms. 
\label{fig:}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
\caption{
velocity gradient of the lens model in the lens plane (left), source plane
(right).
\label{fig:}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SED}

We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak. 
Also do SED fit with IRAS upper limits.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
\caption{TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), extract flux after removing a point source model.
Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction.
Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied. Spitzer/MIPS: PSF fit flux, as source size < native PSF FWHM of 6".
Might want to add NVSS constraints.
 \label{fig:}}
\end{figure*}

\input{table_photometry_AAScustomized}

\end{document}

>>>>

Understanding the baryon cycle has immense implications to our understanding in galaxy evolution...
Despite the recent progress in theoretical models and observational studies...

%observed trend
Studies of galaxy evolution find SFRD and BHAH peak at
$z$$\sim$2 and declines rapidly toward $z$$=$0. A leading explanation for such
a trend is the evolution of molecular gas content and SFE in galaxies (CW13). Due to higher gas fraction than local, regardless of their position in the SFR-M* plane, both MS and SB at high z have depletion time that is much short than local, suggesting more efficient mode for SF. Recent studies also find dynamical evidence for clumpy, globally unstable disks at high-z,
where SF is enhanced by disk instabilities and not mergers (cite: Genzel+05, Forster-Schreiber+09).

While gas-rich systems also exist in local universe, they appear to be
fundamentally different from high-z galaxies.
The local gas-rich systems are also those with the highest IR luminosities, commonly known as ultra-luminous IR galaxies (ULIRGs; \LIR\,$>$\,10$^{12}$\Lsun), nearly of all which appear to be [interacting galaxies/galaxy mergers] in different stages of merging (e.g. Sanders & Mirabel 1996), powered by SB or AGN. While the nature of the power source are still not well-understood.
Regardless of the energy source ((merger-induced) starburst vs AGN accretion), both
are fueled by enormous concentration and supply of molecular gas that has been dynamically driven into the circumnuclear regions. However, it is still unclear what processes...

However, there is a dearth of CO measurements at intermediate redshifts due to observational difficulties, in which the \aco line is redshifted frequency range currently unavailable.
Studying the cold gas at the redshift range 0.2 < z < 1 is important though, as the most dramatic change in star formation activity (e.g. Madau et al. 1998, Hopkins & Beacom 2006). Up to now, very little is known about the molecular gas content at moderate z. The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z > 0.2. With the advance in mm-instruments, Combes+11 investigate the variation of molecuar gas and SFE in an expanded sample of 30 ULIRGs with CO observations.

% quenching
While we know blah at the local universe and studies of the gas properties at
high-z are also emerging in recent years (see CW13 for a review). It is still
unclear what mechanism is responsible for removing cold gas from galaxies and
shutting down their star formation to build-up present-day red sequence
galaxies, leading to a change of slope at high M* (esp. at $z$ $<$ 1.5),  i.e.
suppression of SFR at high M*, i.e. strong evolution in sSFR (of massive gal.)
(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
% Many star formation suppression or "quenching" processes have been suggested, including mergers, ram pressure stripping, tidal ``harassment", etc. One of the more intriguing possibilities, however, is star formation quenching via powerful feedback from AGNs.

% formation of local gal. population
Physically motivated galaxy evolution models find that feedbacks are needed to turn off SF to build-up present day red sequence galaxies. (Dave+05)
Current studies agree that ULIRGs are important in giving rise to local
ellipticals (if mergerd) or spirals with massive bulge (Springel+05). But the formation and evolution is unclear due to the limited spatial resolution available in probing the gas of large sample at $z$$>$0. Ideally, to understand them would require high resolution to probe the kinematics and strucutral properties.
The role of merger in building up the mass of galaxies across the universe.

Based on theoretical grounds, the resulting morphology of the merger will depend mainly intial gas ontent and the mass ratio of the merging galaxies. Gas provides a dissipative component to remove angular momentum and assist colaspe/funnel to the center.s

 -- H2 gas more concentrated towards galactic nucleus in local ULIRGs, which are all mergers (e.g. Sanders & Mirabel 1996).
One explanation to the observed gas concentration toward center: gravitational torques as a result of interactions drive gas towards center towards the circumnuclear regions. SB and BH accretion can then be triggered if the dynamical time-scale is shorter than the feedback mechanisms.

% gas dynamics and AGN growth/ evolution
In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the
progenitors of the dormant SMBHs in nearby galaxies. Quasars are powered by gas falling into central BHs, when galaxies
collide or merge.
On the other hand, it is found that high-z BHs grow faster than their host galaxies since the dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than the inferred one based on local BH-bulge mass relation.
Meaning the Magorrian relation doesn't hold at $z$\,$\gtrsim$ BLAH, which means that we need to also understand the
properties of AGN host galaxies between these epochs.
From local observations, there is no strict relation between presence of an AGN, companions or barred structures, AGN don't
show obvious systemic signatures of nuclear fueling form host. Thus, need to trace dynamics of gas in QSO host galaxies to understand the dynamical processes leading to
gas accumulation/inflow toward center (e.g. bars or merger-driven) for SMBH grow and SB.

(ULIRGS; \LIR\,$>$\,10$^{12}$\Lsun) are typically and display morphological features/evidence such as double-nuclei (with close separation), tidal tails/features, distorted isophotes, rings/ring-like structure.

C06 report the with magnification ~ 9, claimed Seyfert 1 spiral galaxy.

%%%%%%%%%%%%%%%%%%%%%%%%%

\section{IRAC}
For the IRAC channels, the point spread function (PSF) is undersampled and thus photometry was extracted in circular apertures of radius 3?pixels (?3.6?arcsec) with background determined in an annulus of inner radius 12?pixels and outer radius 20?pixels (?14.4?24?arcsec). Apertures were centred on the location of each source as listed in Tables 1 and 2. Array location-dependent corrections were applied to the IRAC photometry. Correction images available online at http://ssc.spitzer.caltech.edu/irac/calibrationfiles/locationcolor/ were mosaicked in the same way as the data frames to produce a correction mosaic.

The aperture photometry of a source was then multiplied by the value of the correction mosaic at the centre of the source image. Aperture corrections were taken from tabulated values listed in the IRAC Data Handbook. Colour corrections were applied by interpolation from tabulated values using the source effective temperatures as listed in Tables 1 and 2.  Absolute calibration of the IRAC is stable to 1?3?per cent (Reach et al. 2005). We add a 3?per cent calibration uncertainty in quadrature to statistical background errors from pixel-to-pixel variation determined in the aperture module to give a final error on the IRAC photometry. The photometry was de-reddened using the values determined by Sanner et al. (2000) converted to IRAC wavelengths using relations of Flaherty et al. (2007). The final photometry is listed in Tables 3 and 4.

%%%%%%%%%%%%%%%%%%%%
CO/H2 conversion factor:
while alphaCO of 0.8 is advocated for ULIRGs.
The conversion factor in these dynamically turbulent system could be different than BLAH since the gas is potentially warmer, more excited, and denser; the conversion factor X\_CO scales as sqrt(n)/T.
